Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-01-10 Tex/Old text/abbreviations.tex
thesis update

\noindent $a$ Ideality or quality factor \\
AC Alternating current \\
$C_{10}$ 10h of rated battery capacity \\
$C_{bank}$ Total capacity of the battery bank \\
CBMC C Bounded Model Checker \\
$ cos \varphi $ Power factor of the inverter \\
CPA Configurable Program Analysis \\
CPAchecker Configurable Program Analysis Checker \\
DC Direct current \\
$DOD$ Depth of discharge ($DOC=1-SOC$) \\
$E_{consumption}$ Energy consumption \\
$E_{corrected}$ Energy corrected \\
$E_{p}$ Energy produced by one panel \\
ESBMC Efficient SMT-based Bounded Model Checker \\
$G$ Solar irradiance \\
$ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$) \\
$I$ Current \\
$I_{0}$ Reverse saturation current \\
$ I_{AC} $ Current that the inverter supply to the house \\
$I_{c,min}$ Charge controller minimum current \\
$ I_{DC} $ Current required by the inverter from the DC source \\
$ I_{in} $ Input current \\
$I_{load}$ Current that feed the load \\
$ I_{out} $ Output current \\
$I_{ph}$ Photocurrent \\
$ I_{ph,ref} $ Photocurrent at STC \\
$I_{pv}$ Current from the PV system \\
$ I_{sc} $ Short-circuit current \\
$ I_{sc,amb} $ Ambient short-circuit current \\
$ I_{sc,ref} $ Short-circuit current at STC \\
$ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); \\
$MAX_{AC,ref}$ Peak power that the inverter can support \\
$N$ Number of series-connected cells \\
$N_{B}total$ Sized number of batteries \\
$N_{BP}$ Sized number of parallel batteries \\
$N_{BP}min$ Total minimum number of parallel batteries \\
$N_{BS}$ Sized number of series batteries \\
$N_{BS}min$ Total minimum number of series batteries \\
NOCT Nominal Operating Cell Temperature \\
$N_{PS}$ Sized number of panels in series \\
$N_{PSmin}$ Total number of panels in series \\
$N_{PP}$ Sized number of panels in parallel \\
$N_{PPmin}$ Total umber of panels in parallel \\
$ N_{TP} $ Sized number of panels \\
$N_{TPmin}$ Total minimum number of needed solar panels \\
PV Photovoltaic \\
P Power \\
$P_{in}$ Input power \\
$P_{out}$ Output power \\
$P_{surge}$ Maximum peak power demanded by house for few seconds \\
$q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $) \\
SAT Satisfiability or Boolean satisfiability problem \\
SAT When returns a failure from the verification tool \\
SMT Satisfiability modulo theories \\
$ SOC $ Battery state of charge \\
STC Standard Test Condition (reference state) \\
$T$ Temperature \\
$ T_{air} $ Ambient temperature \\
$ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$) \\
UNSAT Condition when verification tool succeeds (could not reach an error) \\
V Voltage \\
$ V_{AC}  $ Voltage that the inverter supply to the house \\
$V_{c}$ Battery charge voltage  \\
$V_{d}$ Battery discharge voltage \\
$ V_{DC} $ Input voltage to the inverter delivered by the DC source \\
$ V_{in} $ Input voltage \\
$ V_{oc} $ Open-circuit voltage \\
$ V_{oc,ref} $ Reference open-circuit voltage at STC \\
$ V_{out} $ Output voltage \\
$ V_{system} $ DC voltage of the bus \\
$V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $) \\
$\Delta T$ Temperature variation ($\Delta T=T-T_{ref} $) \\
$ \mu_{I} $ Short-circuit current temperature coefficient ($A/K$) \\
$ \mu_{V} $ Open-circuit voltage temperature coefficient ($ V/K $) \\
$\eta_{b}$ Battery efficiency \\
$\eta_{c}$ Charge controller efficiency \\
$\eta_{i}$ Inverter efficiency \\
$\eta_{p}$ PV panel efficiency \\

>>>>

\noindent $a$ Ideality or quality factor \\
AC Alternating current \\
ANEEL National Electricity Agency (from Brazil) \\
$C_{10}$ 10h of rated battery capacity \\
$C_{bank}$ Total capacity of the battery bank \\
CBMC C Bounded Model Checker \\
CEGIS Counterexample Guided Inductive Synthesis \\
CFA Control-Flow Automata \\
$ cos \varphi $ Power factor of the inverter \\
CPA Configurable Program Analysis \\
CPAchecker Configurable Program Analysis Checker \\
CPES Cyber-Physical Energy Systems \\
CPS Cyber-Physical Systems \\
DC Direct current \\
$DOD$ Depth of discharge ($DOD=1-SOC$) \\
$E_{consumption}$ Energy consumption \\
$E_{corrected}$ Energy corrected \\
$E_{p}$ Energy produced by one panel \\
ESBMC Efficient SMT-based Bounded Model Checker \\
$G$ Solar irradiance \\
$ G_{ref} $ Solar irradiance at STC ($1000 W/m^{2}$) \\
GEF Global Environment Facility \\
HDI Human Development Index \\
IRR  Internal Rate of Return \\
$I$ Current \\
$I_{0}$ Reverse saturation current \\
$ I_{AC} $ Current that the inverter supply to the house \\
$I_{c,min}$ Charge controller minimum current \\
$ I_{DC} $ Current required by the inverter from the DC source \\
$ I_{in} $ Input current \\
$I_{load}$ Current that feeds the load \\
$ I_{out} $ Output current \\
$I_{ph}$ Photocurrent \\
$ I_{ph,ref} $ Photocurrent at STC \\
$I_{pv}$ Current from the PV system \\
$ I_{sc} $ Short-circuit current \\
$ I_{sc,amb} $ Ambient short-circuit current \\
$ I_{sc,ref} $ Short-circuit current at STC \\
$ k_{B} $ Boltzmann constant ($ 1.3806503\times10^{-23}J/K $); \\
LCC  Life Cycle Cost \\
LCOE Levelized Cost of Energy \\
LLP  Loss of Load probability \\
LOLP Loss of Load Probability \\
LPSP Loss of Power Supply Probability \\
$MAX_{AC,ref}$ Peak power that the inverter can support \\
MPPT Maximum Power Point Tracking \\
$N$ Number of series-connected cells \\
$N_{B}total$ Number of sized batteries \\
$N_{BP}$ Number of sized parallel batteries \\
$N_{BP}min$ Total minimum number of parallel batteries \\
$N_{BS}$ Number of sized series batteries \\
$N_{BS}min$ Total minimum number of series batteries \\
NOCT Nominal Operating Cell Temperature \\
NPC  Net Present Cost \\
$N_{PS}$ Number of sized panels in series \\
$N_{PSmin}$ Total number of panels in series \\
$N_{PP}$ Number of sized panels in parallel \\
$N_{PPmin}$ Total umber of panels in parallel \\
$ N_{TP} $ Number of sized panels \\
$N_{TPmin}$ Total minimum number of solar panels needed \\
PV Photovoltaic \\
P Power \\
$P_{in}$ Input power \\
$P_{out}$ Output power \\
$P_{surge}$ Maximum peak power demanded by house for few seconds \\
$q$ Absolute value of the electron's charge ($ -1.60217646\times10^{-19}C $) \\
QF  quantifier-free (formula) \\
RQ Research Question \\
REEEP Renewable Energy and Energy Efficiency Partnership \\
SAT Satisfiability or Boolean satisfiability problem \\
SAT When the verification tool returns a failure \\
SMT Satisfiability module theories \\
$ SOC $ Battery state of charge \\
STC Standard Test Condition (reference state) \\
$T$ Temperature \\
$ T_{air} $ Ambient temperature \\
$ T_{ref}$ Temperature at STC ($=298.15 K$ or $25^{o}C$) \\
UNEP United Nations Environment Programme \\
UNSAT Condition when verification tool succeeds (could not reach an error) \\
V Voltage \\
$ V_{AC}  $ Voltage that the inverter supplies to the house \\
$V_{c}$ Battery charge voltage  \\
$V_{d}$ Battery discharge voltage \\
$ V_{DC} $ Input voltage to the inverter delivered by the DC source \\
$ V_{in} $ Input voltage \\
$ V_{oc} $ Open-circuit voltage \\
$ V_{oc,ref} $ Reference open-circuit voltage at STC \\
$ V_{out} $ Output voltage \\
$ V_{system} $ DC voltage of the bus \\
$V_{T}$ Thermal voltage ($ V_{T}=k_{B}T/q $) \\
$\Delta T$ Temperature variation ($\Delta T=T-T_{ref} $) \\
$ \mu_{I} $ Short-circuit current temperature coefficient ($A/K$) \\
$ \mu_{V} $ Open-circuit voltage temperature coefficient ($ V/K $) \\
$\eta_{b}$ Battery efficiency \\
$\eta_{c}$ Charge controller efficiency \\
$\eta_{i}$ Inverter efficiency \\
$\eta_{p}$ PV panel efficiency \\

### 2020-01-10 Tex/Old text/chapters/appendix.tex
thesis update

%\textbf{List of Publications}
%
Here there are a list of papers that were written during the thesis elaboration and the status of every submission until the date of this document.

@@

Trindade, A., Cordeiro, L. \textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published on-line on 15 October 2019) by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}~\cite{TrindadeCordeiro19}.

@@

\section{Congress}

Trindade, A., Cordeiro, L. \textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 06 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}. This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline in 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.

>>>>

%\textbf{List of Publications}
%
Papers written during thesis elaboration with the status of every submission up to the date of this document.

@@

Trindade, A., Cordeiro, L. \textbf{Automated Formal Verification of Stand-alone Solar Photovoltaic Systems}, submitted: 8 May 2019, status: accepted 26 September 2019; published online 15 October 2019 by Elsevier Solar Energy (Impact Factor 4.674, CAPES A1 Interdisciplinary, CAPES A1 Engineering IV) \url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X1930965X}~\cite{TrindadeCordeiro19}.

@@

\section{Conference}

Trindade, A., Cordeiro, L. \textbf{Automated Formal Synthesis of Optimal Sizing for Stand-Alone Solar Photovoltaic Systems}, submitted: 6 May 2019, status: rejected by The IEEE/ACM Automated Software Engineering (ASE 2019) Conference (New Ideas Papers) in \url{https://2019.ase-conferences.org/track/ase-2019-papers}. This paper is now the base of a new paper, for the 32nd International Conference on Computer-Aided Verification (CAV) 2020 with deadline on 23 January 2020 in \url{http://i-cav.org/2020/call-for-papers/}.

### 2020-01-10 Tex/Old text/chapters/appendixB.tex
thesis update

Here we describe the two tools created with the target to implement and validate the two scientific methodologies of the thesis.

@@

During the Ph.D. process, the techniques from computer science proposed to tackle issues related to solar photovoltaic systems became algorithms and programs. Those programs became tools, and the tools were used during comparative with simulation tools in order to validate the techniques.

One premise of our tools was to be written as an ANSI C program, and to follow the requirements established for the International Competition on Software Verification (SV-COMP) \footnote{https://sv-comp.sosy-lab.org/}. That allow us to write a code that could be executed into three different verifiers without adaptation, and even in the future other verifiers can be used as well.
%
%\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.

Therefore, we wrote the code without the use of '\# include', or '\# define'. Moreover, based on the fact that there exists no use of compiler library, it was necessary to write some functions, which perform specific calculations according to the adopted mathematical models (e.g., logarithm of natural order and exponential).

%---------------------------------------
\subsection{Automated Verification Tool (PV System validation)}
\label{sec:automatedverification}
%---------------------------------------

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and datasheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (e.g., logarithm of natural order, exponential);

@@

\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the state of charge form batteries, committing to deliver the power and energy that the house demands, according with the restrictions form the sized system.
\end{itemize}

%---------------------------------------
\subsection{Automated Synthesis Tool (PV System Optimal Sizing)}
\label{sec:automatedsynthesis}
%---------------------------------------

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and datasheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (start value with the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);

@@

%---------------------------------------
\section{How to use it}
%---------------------------------------

The only block that demands user intervention to input data is the block 1 listed in~\ref{sec:automatedverification} and \ref{sec:automatedsynthesis} from the automated verification and synthesis tools respectively. If it is aimed to change the mathematical model adopted, so coding must be done in block 3 of the automated verification tool and block 2 of the automated synthesis tool.

Regarding the automated verification tool, it is necessary to input the following data (editing and modifying the code):

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item Number of solar panels in series;
\item Number of solar panels in parallel;
\item Number of series-connected cells from each solar panel;
\item Nominal Operating Cell Temperature;
\item Reference solar irradiance;
\item Reference temperature;
\item Short-circuit current temperature coefficient;
\item Open-circuit voltage temperature coefficient;
\item Reference short-circuit current;
\item Reference open-circuit voltage;
\item Reference maximum current, voltage, and power;
\item Minimum MPPT voltage;
\item Operation current;
\item Solar panel efficiency;
\item Panel area in square meters;
\item DC-bus voltage;
\item Individual battery voltage;
\item Battery bank capacity;
\item State of charge limit;
\item Number of batteries in series;
\item Number of batteries in parallel;
\item Autonomy of the batteries;
\item Efficiency from batteries;
\item Float, absorption, and bulk battery voltages;
\item Charge controller efficiency;
\item Charge controller current;
\item Charge controller maximum voltage;
\item Inverter output voltage;
\item Inverter AC reference power;
\item Inverter maximum (surge) AC power reference;
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

Moreover, regarding the automated synthesis tool, it is necessary to add the following data (editing and modifying the code):

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item DC-bus voltage;
\item Autonomy of the batteries;
\item State of charge limit;
\item Individual battery voltage;
\item Reference solar irradiance;
\item Reference temperature;
\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars);
\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars);
\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage output, minimum MPPT voltage, maximum current, cost in US dollars);
\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars);
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

@@

Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the better performance during the comparative than other verifiers. However, in \ref{sec:setup} it was showed how to use the code with other verifiers.

ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}. There is just the Linux version of the verifier.

@@

Where:
\begin{itemize}
\item -no-bounds-check: says to the verifier to not perform array bound check (the aim is not to check array bound violation);
\item -\phantom{}-no-pointer-check: says to the verifier to not check if there is pointer violation;
\item -\phantom{}-unwind 100: it limits the bound of search (100 in this case);
\item -\phantom{}-smt-during-symex: enable incremental SMT solving;
\item -\phantom{}-smt-symex-guard: call the solver during symbolic execution;
\item -\phantom{}-z3: uses Z3 as solver.
\end{itemize}

Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when performing the case studies.

@@

Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented better performance during the comparative than other verifiers. However, in \ref{sec:synthesissetup} it was showed how to use the code with other verifiers.

The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available to Linux and MS-Windows operational systems.

@@

Note that the default heap size is 1200m (or 1.2 GB of RAM). However, it is indicated to specify a significant value with '-heap' if you have more RAM available. In our case, we adjusted the heap to 64000m (64 GB).

Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' at the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value. In our case, 'limits.time.cpu = 14400s', i.e., 14400 seconds or 240 minutes or 4 hours.

Some results, reports, and graphics, issued by the CPAchecker verifier were depicted in \ref{sec:synthesisresults}.

>>>>

Here we describe the two tools created to implement and validate the two scientific methods/techniques of the thesis.

@@

During the doctoral process, the techniques from computer science proposed to deal with issues inherent to solar photovoltaic systems became algorithms and programs. These programs became tools, and the tools were used for the purpose of comparison with simulation tools in order to validate the techniques.

One premise of our tools was that they will be written as an ANSI C program, and to follow the requirements established for the International Competition on Software Verification (SV-COMP) \footnote{https://sv-comp.sosy-lab.org/}. This allows us to write a code that can be executed into three different verifiers without adaptation, with the possibility that in the future, other verifiers can also be used.
%
%\textcolor{red}{the second part of this sentence is unclear...} In general, we pursuit to write code that could be verification tool independent, i.e., that can be used in any model checking tool without adaptation, since we aimed to evaluate different.

With this in mind, the code was written without using of '\# include', or '\# define'. Moreover, based on the fact that a compiler library is not used, it was necessary to write in some functions which perform specific calculations depending on the mathematical models adopted (e.g. natural logarithms and exponents).

%---------------------------------------
\subsection{The Automated Verification Tool (for PV System validation)}
\label{sec:automatedverification}
%---------------------------------------

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from the location (minimum and maximum solar irradiance and temperature, for 24 hours of the day) as array, requirements, and datasheet information pertaining to each item of equipment of the PV system to be verified;

\item \textbf{Block 2}: support functions (e.g. natural logarithms,  exponents);

@@

\item \textbf{Block 4}: main code with charge, discharge battery control, based on PV generation from solar panels and the battery state of charge, committing to deliver the power and energy that the house requires, in  accordance with the restrictions from the sized system.
\end{itemize}

%---------------------------------------
\subsection{The Automated Synthesis Tool (for PV System Optimal Sizing)}
\label{sec:automatedsynthesis}
%---------------------------------------

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from the location, user requirements, and datasheet information on each item of equipment of the PV system to be verified;

\item \textbf{Block 2}: support functions (start value at the lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);

@@

%---------------------------------------
\section{Instructions on How to Use it}
%---------------------------------------

The only block that requires user intervention to input data is Block 1 listed in~\ref{sec:automatedverification} and \ref{sec:automatedsynthesis} from the automated verification and synthesis tools respectively. If the intention is to change the mathematical model adopted, coding must be done in Block 3 of the automated verification tool Block 2 of the automated synthesis tool.

For the automated verification tool, it is necessary to input the following data (editing and modifying the code):

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24 hours of the day) at location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours per day at the location);
\item Number of solar panels in series;
\item Number of solar panels in parallel;
\item Number of series-connected cells from each solar panel;
\item Nominal Operating Cell Temperature;
\item Reference solar irradiance;
\item Reference temperature;
\item Short-circuit current temperature coefficient;
\item Open-circuit voltage temperature coefficient;
\item Reference short-circuit current;
\item Reference open-circuit voltage;
\item Reference maximum current, voltage, and power;
\item Minimum MPPT voltage;
\item Operation current;
\item Solar panel efficiency;
\item Panel area in square meters;
\item DC-bus voltage;
\item Individual battery voltage;
\item Battery bank capacity;
\item State of charge limit;
\item Number of batteries in series;
\item Number of batteries in parallel;
\item Battery autonomy;
\item Battery efficiency;
\item Float, absorption, and bulk battery voltages;
\item Charge controller efficiency;
\item Charge controller current;
\item Charge controller maximum voltage;
\item Inverter output voltage;
\item Inverter AC reference power;
\item Inverter maximum (surge) AC power reference;
\item AC voltage (standard voltage from outlet);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

in the case of the automated synthesis tool, the following data must be added (editing and modifying the code):

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24 hours of the day) at location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours per day at the location);
\item DC-bus voltage;
\item Battery autonomy;
\item State of charge limit;
\item Individual battery voltage;
\item Reference solar irradiance;
\item Reference temperature;
\item For every item on the solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in USD);
\item For every item on the battery list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in USD);
\item For every item on the charge controller list, as a matrix (efficiency, nominal current, voltage output, minimum MPPT voltage, maximum current, cost in USD);
\item For every item on the inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in USD);
\item AC voltage (standard voltage from outlet);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

@@

Here we describe precisely how to use the code explained in the previous section (\ref{sec:automatedverification}) using the incremental ESBMC with the Z3 SMT solver that presented the best performance during the comparison with other verifiers. However, in \ref{sec:setup} it was shown how to use the code with other verifiers.

ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}. There is only the Linux version of the verifier.

@@

Where:
\begin{itemize}
\item -no-bounds-check: says to the verifier to not perform array bound check (the aim is not to check array bound violation);
\item -\phantom{}-no-pointer-check: says to the verifier to not check if there is pointer violation;
\item -\phantom{}-unwind 100: limits the bound of search (100 in this case);
\item -\phantom{}-smt-during-symex: enables incremental SMT solving;
\item -\phantom{}-smt-symex-guard: calls the solver during symbolic execution;
\item -\phantom{}-z3: uses Z3 as solver.
\end{itemize}

Some results issued by the ESBMC verifier were shown in \ref{sec:ESBMCverification} when conducting the case studies.

@@

Here we describe precisely how to use the code explained in previous sections (\ref{sec:automatedsynthesis}) using CPAchecker with MathSAT solver, which presented the best performance during the comparison with other verifiers. However, in \ref{sec:synthesissetup} it was shown how to use the code with other verifiers.

The CPAchecker can be downloaded from its web site in \url{https://cpachecker.sosy-lab.org/}. There are versions available for Linux and MS-Windows operational systems.

@@

Note that the default heap size is 1200m (or 1.2 GB RAM). However, specifying a significant value with '-heap' is recommended if you have more RAM available. In our case, we adjusted the heap to 64000m (64 GB).

Another important issue is the time-out of the execution process: the parameter 'limits.time.cpu' in the file 'resource-limits.properties' in folder 'config/includes' must be edited according to the desired value. In our case, 'limits.time.cpu = 14400s', i.e. 14400 seconds or 240 minutes or 4 hours.

Some results, reports, and graphics, issued by the CPAchecker verifier were illustrated in \ref{sec:synthesisresults}.

### 2020-01-10 Tex/Old text/chapters/chapter02.tex
thesis update

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
\centering
\caption{Unregulated standalone SPV system with DC load. Source: \cite{Roy}.}
\label{fig:unregSPV}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
\centering
\caption{Regulated standalone SPV system with DC load. Source: \cite{Roy}.}
\label{fig:regSPV1}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
\centering
\caption{Regulated standalone SPV system with battery and DC load. Source: \cite{Roy}.}
\label{fig:regSPV2}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
\centering
\caption{Regulated standalone system with battery, AC load. Source: \cite{Roy}.}
\label{fig:regSPV3}
\end{figure}

@@

The design and validation of a SPV system can be done by hand or with the aid of a software tool.

In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the SPV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, and to complex financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

@@

The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOC=1-SOC $.

>>>>

\begin{figure}[h]
\includegraphics[width=0.6\textwidth]{unregulatedSPV.png}
\centering
\caption{Unregulated standalone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:unregSPV}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV1.png}
\centering
\caption{Regulated standalone solar PV system with DC load. Source: \cite{Roy}.}
\label{fig:regSPV1}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV2.png}
\centering
\caption{Regulated standalone solar PV system with battery and DC load. Source: \cite{Roy}.}
\label{fig:regSPV2}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{regulatedSPV3.png}
\centering
\caption{Regulated standalone PV system with battery, AC load. Source: \cite{Roy}.}
\label{fig:regSPV3}
\end{figure}

@@

The design and validation of a solar PV system can be done by hand or with the aid of a software tool.

In order to address different aspects of a project system and system's design, a lot of public domain and commercial software is available for the solar PV market. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimation, to site survey and system design tools, and to complex financial analysis software (with optimization). Some tools also provide support to rebate program applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

@@

The ratio between $ Q $ and $ C $ represents the depth of discharge ($ DOD $) or the fraction of discharge, i.e., $ DOD=1-SOC $.
